### 2022-11-29 dissertation/chapters/09-conclusion.tex
🚧 (final-review): Chapter 8 WIP

Chapters \ref{chap:anns}-\ref{chap:probability} provided the reader with the relevant background information that is necessary to develop the novel \acs{BHH}. Chapter~\ref{chap:anns} provided background information on \acp{ANN}. All the components that make up the \acs{AN} were provided and is followed by discussions on \acp{FFNN}. Chapter~\ref{chap:heuristics} provided background information on various low-level heuristics that are designed to train \acp{FFNN}. A number of gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics were presented in detail. Chapter~\ref{chap:hhs} provided background information and literature reviews on \acp{HH}. Meta-learning is discussed and a \acs{HH} classification scheme, developed by \citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, was discussed in detail. Chapter~\ref{chap:probability} provided background information and mathematical derivations on probability theory and Bayesian statistics. Various probability distributions were provided along with their conjugate priors. \acs{MLE} and \acs{MAP} were presented in detail along with mathematical breakdowns.

@@

Similar to the move acceptance strategy, throughout the presentation of the empirical results, it is mentioned that an early stopping strategy can be used to hault the training process if the performance does not improve for a number of steps. In this dissertation, a number of examples were presented where divergence of training loss occurred. Furthermore, a number of examples were presented where overfitting occurred. An early stopping strategy can help prevent such outcomes.

>>>>

Chapters \ref{chap:anns} to \ref{chap:probability} provided the reader with the relevant background information that is necessary to develop the novel \acs{BHH}. Chapter~\ref{chap:anns} provided background information on \acp{ANN}. All the components that make up the \acs{AN} were provided and is followed by discussions on \acp{FFNN}. Chapter~\ref{chap:heuristics} provided background information on various low-level heuristics that are designed to train \acp{FFNN}. A number of gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics were presented in detail. Chapter~\ref{chap:hhs} provided background information and literature reviews on \acp{HH}. Meta-learning is discussed and a \acs{HH} classification scheme, developed by \citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, was discussed in detail. Chapter~\ref{chap:probability} provided background information and mathematical derivations on probability theory and Bayesian statistics. Various probability distributions were provided along with their conjugate priors. \acs{MLE} and \acs{MAP} were presented in detail along with mathematical breakdowns.

@@

Similar to the move acceptance strategy, throughout the presentation of the empirical results, it is mentioned that an early stopping strategy can be used to halt the training process if the performance does not improve for a number of steps. In this dissertation, a number of examples were presented where divergence of training loss occurred. Furthermore, a number of examples were presented where overfitting occurred. An early stopping strategy can help prevent such outcomes.
